Sequential algorithms to split and merge large 3D images

### 2017-05-29 paper.tex
Note on compression and memo on authors

\begin{abstract}
\todo{The abstract goes here. DO NOT USE SPECIAL CHARACTERS, SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.}
\end{abstract}

@@

\subsection{Benchmark}

>>>>

\begin{abstract}
  \todo{The abstract goes here. DO NOT USE SPECIAL CHARACTERS,
    SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.}  Authors (final order
  to be discussed when the paper shapes up): Yongping/Val\'erie,
  Yuhong Yan, Tristan. Perhaps Pierre Bellec.
\end{abstract}

@@

\subsection{Lossless compression}

Lossless compression might reduce overall read and write times by
reducing seek time and data sizes. However, it needs to be implemented
on-the-fly, i.e., in chunks. See the work in~\cite{rajna2015speeding}
and \href{https://github.com/pauldmccarthy/indexed\_gzip}{corresponding
  implementation}.

\subsection{Implementation and Benchmark}
